Hello there! Did you stumble across this phrase by accident, 
or are you looking for what I think you're looking for?
For every page you turn over in this book,
I feel that there is at least one person who deserves to be thanked 
a thousand times over for their continued love, sacrifices and support.
So here we go, until the end of the book: Thank you! Thank you!
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you! 
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!
Thank you! Thank you! Okay, enough with the silly business.
\newperson
\newperson
Yvan, you are an incredible supervisor and group leader.
You always tell the baby PhD students that the first step in a PhD
is not learning to write well, but learning to like to write.
Those words are amazing PhD training wheels.
\newperson
\newperson
Katleen, thank you for your dedication and perseverance
in guiding me and making sure I got off to a good start in my PhD.
I see exciting times ahead for the KDP group, which is overflowing
with enthusiasm and inspiration. I wonder what the future will bring!
\newperson
\newperson
Frank, thank you for giving me the opportunity to start on this journey.
You are an inexhaustible source of new ideas
which often explore the very thin line
between ingenuity and complete insanity.
\newperson
\newperson
Jo, sorry for spilling coffee on your shoes on my first day in Blok B.
My strategy seemed to have worked, for suddenly I had a fourth promotor!
I thoroughly enjoyed my time as an unofficial member of your group.
You are a true people's person; you bring out the best in everybody.
\newperson
\newperson
Joeri, we've come full circle. You brought me into this whole adventure
with your incredible friendliness and that darned oversized pumpkin;
and now, with you as my jury member, you helped me reach my goal.
Let's stay in touch :)
\newperson
\newperson
Wouter, I cannot imagine a better partner to do a PhD with.
If we were genes, I'm sure we would be reciprocal activators,
constantly stimulating each other to do just a little bit more!
Yet, our knowledge was often so perfectly complementary;
if we were a PCA plot, you'd be PC1 and I'd be PC2.
Or maybe the other way around? Let's take turns being PC1 and PC2.
\newperson
\newperson
Sofie, you saved my rear-end from embarrassing moments more frequently than I dare to admit.
The perfect example was when I walked in the MMM on 2014-01-06,
I arrived a little bit too late, and you send me a message:
"You do know that you have to present today, right?"
\newperson
\newperson
Helena, thank you for being such a lovely colleague and an even better friend.
I enjoy our scientific talks and our non-scientific walks.
Together with you, I played the longest ongoing game of hide-and-seek,
on page 22-9 you probably already found the truc that I am referring to.
\newperson
\newperson
Paulina, like a soft summer wind you passed through our lives.
Thanks for putting so many healthy “vege-tables” and strange Polish delicacies in our fridge,
for cycling together to work, and for making weird noises at Remi.
I'm looking forward to the next time we meet, so you can be amazed at how much Remi has grown.
\newperson
\newperson
A big thank you to all the Dambini's for taking care of me while I was hard at work:
An,ArS,ArG,Art,C,D,H,I,Ja,Jon,Jor,Ka,Ke,Li,Lo,M,N,Pa,Pi,Q,RVd,RB,Ru,Sa,Sl,So,St,W,Y.
I'm grateful to be part of such a dynamic and fun group;
you all make hard work at the VIB feel like a walk in the park.
\newperson
\newperson
Miriam, thanks for always being there for us, 
during the good times but also during times of need.
As part of our family, there will always be a spot for you in our house.
Let it be a while until one of us has to organise another reception.
\newperson
\newperson
Because relaxing is as important as work,
a special thanks to a selection of the finest friends.
Laure, Michael, Jasper \& Lize for haut cuisine fun veggie nights.
Joke, Niels \& Kai for exploring dungeons with trolls and lizards together.
Marta, Jan, Tristan \& Rafaël for the many tasty brunches and classy parties.
Mara Marrainne, Sepperd \& Alice for all the unforgettable family moments with our cute kids.
Daan, Mieke \& Lou
Sophie and Marc for entertaining Caro while Elias, Charlotte and I play Minecraft together.
\newperson
\newperson
Cedric, no time difference or distance can keep us apart,
or change our habit to forget the world during our gaming and conversations. 
놀라운 사람과 최고의 친구가되어 주셔서 감사합니다
\newperson
\newperson
My warm thoughts go to:
Vanessa, Marilou, Franco, Alain, Luc, Malika, Sien, Silke, Liam
Anne, Patrick, Evelyne, Stefaan, Steven, Joke, Paul, Tania, Arne, Laure, Lukas, Lise, Dorian
\newperson
\newperson
To mama and papa Jean Paul, thank you for all your love.
You gave me a carefree youth and a good set of morals,
and allowed me to study for as long as I liked.
For all these things and so much more, I can never repay you.
\newperson
\newperson
Papa Chris, I always enjoy talking to you, such as the countless
chess games that we played, and the late night discussions by my bedside.
You made me think for myself and have an opinion of my own.
At the right time, I will pass on the torch to Remi.
\newperson
\newperson
Victor, you're the most adventurous of us three brothers.
Maybe you don't know yet what life will bring, and that's okay. None of us do.
I enjoy driving other people absolutely nuts with our crazy talk.
Thanks for all the memes :)
\newperson
\newperson
Hendrik, as the one who I always looked up to, I blame you for getting me interested
in computers. With you taking computers apart on the table, how could I resist.
I know you paid dearly for this, though, since you would continuously have to
repair the \textit{Windows Me} installation that I just destroyed.
\newperson
\newperson
Ingeborg, Elke and Gallina, thank you for your hospitality and tasty food.
You are all amazing women
for all I know, dealing with a Cannoodt,
requires a special kind of patience.
\newperson
\newperson
To Amor, a big thank you for contributing countless cuddles and endless drool.
I guesstimate at least 50\% of the dissertation was written with you on my lap.
\newperson
\newperson
Hello Petit Remi! 
You're only seven months old, but it feels like I've known you for much longer already.
Your spontaneous happiness when you see me come downstairs 
from a hard day of work immediately makes my day.
\newperson
\newperson
Dear Caro,
I cannot imagine a better partner and mother than you.
You are a strange combination of being extremely thoughtful and caring,
yet you roll over laughing when I stub my toe against the side of the table.
Let's get back on track collecting doorsteps,
and spending time doing the things we love, just us three.
I look forward to the rest of our lives together,
my strong independent woman.
























































































































































































































































































































































































































































































































































































































































































































































































































































1
