























Hello there! Did you stumble across this phrase by accident,\\or are you looking for what I think you're looking for?
For every page you turn over in this book,\\I feel that there is at least one person who deserves to be thanked 
a thousand times over for their continued love, sacrifices and support.\\So here we go, until the end of the book: Thank you! Thank you!
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!\\Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!\\Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!
Thank you! Thank you! Thank you! Thank you! Thank you! Thank you!\\Okay, enough with the silly business. 
Go to the next chapter for more acknowledgements.





















Yvan, you are an incredible supervisor and group leader.\\You always tell the baby PhD students that the first step in a PhD
is not learning to write well, but learning to like to write.\\Those words are amazing PhD training wheels.
Katleen, thank you for your dedication and perseverance\\in guiding me and making sure I got off to a good start in my PhD.
I see exciting times ahead for the KDP group, which is overflowing\\with enthusiasm and inspiration. I wonder what the future will bring!
Frank, thank you for giving me the opportunity to start on this journey.\\You are an inexhaustible source of new ideas
which often explore the very thin line\\between ingenuity and complete insanity.
Jo, sorry for spilling coffee on your shoes on my first day in Blok B.\\My strategy seemed to have worked, for suddenly I had a fourth promotor!
I thoroughly enjoyed my time as an unofficial member of your group.\\You are a true people's person; you bring out the best in everybody.
Joeri, you brought me into this whole adventure\\with your incredible friendliness and that darned oversized pumpkin;
and now, with you as my jury member, you helped me finish my PhD adventure.\\We've truly come full circle.
Go to the next chapter for more acknowledgements.





















































Wouter, I cannot imagine a better partner to do a PhD with. If we were genes,\\we'd be reciprocal activators, constantly stimulating each other to do just a little bit more!
Yet, our knowledge was often so perfectly complementary; if we were a PCA plot,\\you'd be PC1 and I'd be PC2. Or the other way around? Let's take turns being PC1 and PC2.
Sofie, you saved my rear-end from embarrassing moments more frequently than I dare\\ to admit. The perfect example was when I walked in the MMM on 2014-01-06,
I arrived a little bit too late, and you send me a message:\\"You do know that you have to present today, right?"
Helena, thank you for being such a lovely colleague and an even better friend.\\I enjoy our scientific talks and our non-scientific walks.
Together with you, I played the longest ongoing game of hide-and-seek,\\on page 22-9 you probably already found the truc that I am referring to.
Paulina, like a soft summer wind you passed through our lives.\\Thanks for putting so many healthy “vege-tables” and strange Polish delicacies in our fridge,
for cycling together to work, and for making weird noises at Remi.\\I look forward to the next time we meet; you will be amazed at how much Remi has grown.
A big thank you to all the Dambini's for taking care of me while I was hard at work:\\An,ArS,ArG,Art,C,D,H,I,Ja,Jon,Jor,Ka,Ke,Li,Lo,M,N,Pa,Pi,Q,RVd,RB,Ru,Sa,Sl,So,St,W,Y.
I'm grateful to be part of such a dynamic and fun group;\\you make hard work at the VIB feel like a walk in the park.
Go to the next chapter for more acknowledgements.

Because relaxing is as important as work,\\a special thanks to a selection of the friends and family.
Laure, Michael, Jasper \& Lize, thank you for the haut cuisine fun veggie nights.
Joke, Niels \& Kai, thank you for exploring dungeons with trolls and lizards together.
Marta, Jan, Tristan \& Rafaël, thank you for the many tasty brunches and classy parties.
Mara Marrainne, Sepperd \& Alice, thank you for all\\the unforgettable family moments with our cute kids.
Daan, Mieke \& Lou, thank you for taking matters in your own hands\\and upgrading our friendship status into family.
Sophie and Marc, thank you for entertaining Caro\\while Elias, Charlotte and I play Minecraft together. 
Bart, thank you for being such a good friend\\and listening to me when I needed it the most.
Miriam, thank you for always being there for us,\\during the good times but also during times of need.
As part of our family, there will always be a spot for you in our house.\\Let it be a while until one of us has to organise another reception.
Cedric, no time difference or distance can keep us apart,\\or change our habit of forgetting the world around us during our gaming and conversations. 
놀라운 사람과 최고의 친구가되어 주셔서 감사합니다
Big hugs for my family who supported me (Vanessa, Marilou, Franco, Alain,\\Luc, Malika, Sien, Silke, Liam, Anne, Patrick, Evelyne, Stefaan, Arne, Laure, 
Paul, Tania, Dorian, Steven, Joke, Lukas, Lise), and often had to miss me at family parties.
To mama and papa Jean Paul, thank you for all your love.\\You gave me a carefree youth and a good set of morals,
and allowed me to study for as long as I liked.\\For all these things and so much more, I can never repay you.
Papa Chris, I always enjoy talking to you, such as the countless\\chess games that we played, and the late night discussions by my bedside.
You made me think for myself and have an opinion of my own.\\At the right time, I will pass on the torch to Remi.
Victor, you're the most adventurous of us three brothers.\\Maybe you don't know yet what life will bring, and that's okay. None of us do.
I enjoy driving other people absolutely nuts with our crazy talk.\\Thanks for all the memes :)
Hendrik, as the one who I always looked up to, I blame you for getting me interested\\in computers. With you taking computers apart on the table, how could I resist.
I know you paid dearly for this, though, since you would continuously have to\\repair the \textit{Windows Me} installation that I just destroyed.
Ingeborg, Elke and Gallina, thank you for your hospitality and tasty food.\\You are all amazing women
for all I know, dealing with a Cannoodt,\\requires a special kind of patience.
Go to the next chapter for more acknowledgements.







To Amor, a big thank you for contributing countless cuddles and endless drool.
I guesstimate at least 50\% of the dissertation was written with you on my lap.
Hello Petit Remi! You're only seven months old,\\but it feels like I've known you for much longer already.
Your spontaneous happiness when you see me come downstairs\\from a hard day of work immediately makes my day.
Dear Caro, I cannot imagine a better partner and mother than you.\\You make me want to be the best version of myself.
Let's get back on track collecting doorsteps,\\and doing the things we love doing, just us three.
























































































































































































































































































































































































































































































































































































































































































































































































































































1
